Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-07-16 article/index.Rmd
marked rendered article as preprint

>>>>

This is a preprint: the version of the paper that was accepted for publication. Please see the following reference for the final, published version:

Schmid, C. (2019). Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and Northwestern Europe using radiocarbon data. Adaptive Behavior. https://doi.org/10.1177/1059712319860842

Please note that the numerical results of the Mantel statistics are not exactly the same here compared to the final, published version. The Mantel test is a nondeterministic algorithm.
